\textbf{Designing a Virtual Security Management Layer for Cloud Content}

### 2016-02-02 tex/paper.tex
Added some consequences of multiple accesses

Copy-on-Write is used in for example virtual memory management systems~\cite{VIRTCOW}, for snapshot
and as an optimisation technique for objects and types in several programming
languages\cite{LANGCOW}.

Its principle is that when processes or nodes share data in between each other, the data is not
copied until one of the processes does changes to it. This is an optimisation as the processes does
not have to send or copy all of the related data that is in memory, rather they only have to send
pointers to the data. After many Copy-on-Write's a complex tree structure can be built up, but
optimisations can be done to simplify that structure~\cite{COPYONWRITE2}.

@@

\subsection{Terms}
\subsubsection{Snapshot}
A snapshot is a way to record the full state of a system at a specific time. The term comes from
photography where a photo can be seen as the state of what the photo is of, at a certain time.
Snapshots should not be confused with full copies of a system as full copies can be used as backups
meanwhile snapshots are not very effective means of backups in the case of data corruption. It is
not effective against data corruption as snapshots usually still refer to unchanged data that is
still a part of the system~\cite{SNAPSHOT}.

@@

There could also be another relevant model done to show that content can not be accessed by
unauthorized viewers once the content is uploaded to a CDN, but as that should already have been
thoroughly checked by the CDN providers this work can focus solely on the internal users and content
of the management system.

\subsection{Related work}
\fix Write about Bell-Lapadula et. al
The model for this paper is based on the work that was done by Bell, D Elliott, LaPadula and Leonard
J in their papers Secure computer systems: Mathematical foundations~\cite{BLP1} and Secure computer
systems: A mathematical model~\cite{BLP2}. In these papers the foundation is laid for how to model
a computer system to be able to analyse the security of a system. Furthermore this paper was also 
inspired by Biba, Integrity considerations for secure computer systems~\cite{BIBA}, where many of 
the points made by him was taken into consideration when inspecting that the integrity of the data 
was always sound.

@@

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        Set & Elements & Semantics \\ \hline
        C   & $c_0\dots c_n$                & Containers; folders in the virtual file system\\ \hline
        F   & $f_0\dots f_n$                & Files; files, images, videos\\ \hline
        M   & $m_0\dots m_n$                & Content; Meta-data for files\\ \hline
        U   & $u_0\dots u_n$                & Users; registered users in the system\\ \hline
        A   & $A[u_0,c_0]\dots A[u_n, c_n]$ & Access matrix; describes what containers users have access to\\ \hline
    \end{tabular}
\end{center}

@@

@@

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        Action & Semantics \\ \hline
        u, read(o)            & User u reads object o\\ \hline
        u, write(o)           & User u writes object o\\ \hline
        u, copy(o)            & User u copies object o and the copy gets a new ID\\ \hline
        u, change(o)          & User u locally changes object o \\ \hline
        u, modify(o)          & User u globally modifies object o\\ \hline
        u, modify(o', o)      & User u globally modifies object o based on object o'\\ \hline
        u, delete(o)          & User u deletes object o\\ \hline
        u, snapshot(o)        & User u takes a snapshot of object o \\ \hline
    \end{tabular}
\end{center}

\fix Translate to mathematical expressions
\subsubsection{Consequences of modification}
\begin{equation} \label{eq:fileupdate}
    \begin{split}
        m' & = u, read(m) \land \\
        x  & = f \in m' \land \\
        f' & = u, change(x) \land \\
        u, & write(f') \land \\
        u, & modify(f', m) \Implies f \in F \land f' \in F
    \end{split}
\end{equation}
If a user wants to update a file in a content, the file is copied and the original is intact.

@@

>>>>

Copy-on-Write is used in for example virtual memory management systems~\cite{VIRTCOW}, snapshot
algorithms and as an optimisation technique for objects and types in several programming
languages\cite{LANGCOW}.

Its principle is that when processes or nodes share data in between each other, the data is not
copied until one of the processes makes changes to it. This is an optimisation as the processes does
not have to send or copy all of the related data that is in memory, rather they only have to send
pointers to the data. After many Copy-on-Write's a complex tree structure can be built up, but
optimisations can be done to simplify that structure~\cite{COPYONWRITE2}.

@@

\subsection{Terms}
\subsubsection{Snapshot}
A snapshot is a way to record the full state of a system at a specific time. The term comes from
photography where a photo can be seen as the state of what the photo is of, at a certain time.
Snapshots should not be confused with a full copy of a system, or part of a system, as full copies 
can be used as backups meanwhile snapshots are not very effective means of backup in the case of 
data corruption. It is not effective against data corruption as snapshots usually still refer to 
unchanged data that is still a part of the system~\cite{SNAPSHOT}.

@@

There could also be another relevant part included in the model, to show that content can not be 
accessed by unauthorized viewers once the content is uploaded to a CDN. But as that should already 
have been thoroughly checked by the CDN providers this work can focus solely on the internal users 
and content of the management system.

\subsection{Related work}
The model for this paper is based on the work that was done by Bell, D Elliott, LaPadula and Leonard
J in their papers Secure computer systems: Mathematical foundations~\cite{BLP1} and Secure computer
systems: A mathematical model~\cite{BLP2}. In these papers the foundation was laid for how to model
a computer system to be able to analyse the security of a system. Furthermore this paper was also 
inspired by Biba, Integrity considerations for secure computer systems~\cite{BIBA}, where many of 
the points made by him was taken into consideration when inspecting that the integrity of the data 
was always sound.

@@

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Set} & \textbf{Elements} & \textbf{Semantics} \\ \hline
        C   & $c_0\dots c_n$                & Containers; folders in the virtual file system\\ \hline
        F   & $f_0\dots f_n$                & Files; files, images, videos\\ \hline
        M   & $m_0\dots m_n$                & Content; Meta-data for files\\ \hline
        U   & $u_0\dots u_n$                & Users; registered users in the system\\ \hline
        A   & $A[u_0,c_0]\dots A[u_n, c_n]$ & Access matrix; describes what containers users have access to\\ \hline
    \end{tabular}
\end{center}

@@

% The last one means that no users can delete actual files

@@

\subsection{Consequences of modification}
\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Action} & \textbf{Semantics} \\ \hline
        u, read(o)            & User u reads object o\\ \hline
        u, write(o)           & User u writes object o\\ \hline
        u, copy(o)            & User u copies object o and the copy gets a new ID\\ \hline
        u, change(o)          & User u locally changes object o \\ \hline
        u, modify(o', o)      & User u globally modifies object o based on object o'\\ \hline
        u, delete(o)          & User u deletes object o\\ \hline
        u, snapshot(o)        & User u takes a snapshot of object o \\ \hline
    \end{tabular}
\end{center}

\begin{equation} \label{eq:fileupdate}
    \begin{split}
        m' & = u, read(m) \land \\
        x  & = f \in m' \land \\
        f' & = u, change(x) \land \\
        u, & write(f') \land \\
        u, & modify(f', m) \Implies f \in F \land f' \in F
    \end{split}
\end{equation}
If a user wants to update a file in a content, the file is copied and the original is intact.

@@

\begin{equation} \label{eq:delete}
    \begin{split}
        f' = f \in (u, read(c)),  \\
        u, delete(c) \Implies \\
        c \not \in C \land f' \in F
    \end{split}
\end{equation}
If a user deletes content, the file referred to in the content is not deleted.

\subsection{Interaction of Multiple Accesses}
\fix Rename consequence?

As a result of consequence~\ref{eq:contentupdate} and ~\ref{eq:containerupdate} there can be race
conditions where the last write wins. This could be solved by locks or transactions, but as updates
are not based on each other, the trade-off for this inconsistency to scalability and speed is
intentional. However as can also be seen in consequence~\ref{eq:fileupdate}, if a file is
removed from a content that file is not removed from the set of files, even though its modification
process is not the last one to write to the content. This is necessary as a file can be referenced
from several content and the removal process can not atomically ensure that the file is not referred
to by another content. This results in a lot of files in the system which are not referenced from
anywhere. This can be solved by either making each file keep track of how many times it is referred
to and also make it possible to check this number and delete the file in an atomic fashion. An
easier approach would be to have a garbage collector which locks parts of the system momentarily
meanwhile it removes files which are not referenced.
